---
title: "PSYR6003-Assignment-2"
author: "Colby Price"
format: html
editor: visual
---

```{r}
#First, to load all the packages that I may require:
library(flexplot)
library(haven)
library(tidyverse)

#loading that .sav file
perfect <- read_sav("PSYR6003.A2.sav")
#lets view this data
view(perfect)
#joy

#Want to convert that weird string to a factor variable
perfect.NB <- perfect %>% 
mutate(sex = as.factor(sex))
perfect.NB <- filter(perfect.NB, sex == "Male" | sex == "Female")
#I'm wanting to make sure this worked. so:
print(perfect.NB$sex)
#Neat. It'll do that stuff in the background

#Want to put the subscale scores in there, meaning the means:
#First, reverse code that reverse variable
perfect.NBS <- perfect.NB %>% 
mutate(across(matches("tipm.CONS2.3y"), ~ 8 - .))
#lets view this data to see if I messed up
view(perfect.NBS)
#like the data set, perfect

#Finally, let's start mutating the mean subscale scores:
perfect.NBSM <- perfect.NBS %>% 
  mutate(mps.mean = rowMeans(across(starts_with("mps")), na.rm = FALSE), 
         negative.mean = rowMeans(select(perfect.NB, guilt1.3y:host3.3y), na.rm = FALSE),
         tipm.mean = rowMeans(across(starts_with("tipm")), na.rm = FALSE))
#to make sure I didn't mess up again:
view(perfect.NBSM)
```

Research Question: What is the impact of sex, conscientiousness, and SPP on negative affect? *&/or*\
Does SPP impact negative affect more than sex and conscientiousness?

Linear Model: Negative Affect = b~0~ + (Sex \*\* b~1~) + (Conscientiousness \*\* b~2~) + (SPP \*\* b~3~) + E\
Parameter(s) of Interest: Negative Affect = b~0~ + (Sex \*\* b~1~) + (Conscientiousness \*\* b~2~) + **(SPP \*\* b~3~)** + E

Model Comparison: Negative Affect = b~0~ + (Sex \*\* b~1~) + (Conscientiousness \*\* b~2~) + (SPP \*\* b~3~) + E\
Negative Affect = b~0~ + (Sex \*\* b~1~) + (Conscientiousness \*\* b~2~) + E

```{r}
#1.) Visualize the univariate distributions
#reduced:
flexplot(negative.mean~mps.mean+tipm.mean | sex, data = perfect.NBSM)
#full:
flexplot(negative.mean~tipm.mean | sex, data = perfect.NBSM)

#Visualize the assumptions
Full <- lm(negative.mean~mps.mean+tipm.mean | sex, data = perfect.NBSM)
visualize(Full, plot = "residuals")
```
